Estimating the dynamics of SPARQL query results using binary classification

### 2019-08-05 main.tex
clarifying this: On page 12, a random baseline is used as a reference. Was the yes/no random guess adjusted to the apriori probability of results to change?

\paragraph{Results:} Table~\ref{tab:classifier} shows the $F_1$-score for the predictions made considering the union of different combinations of the sets of features (\textsc{q}, \textsc{p}, \textsc{r}) and varying the window sizes (3, 5, 9, 17); for reference, we include a baseline that randomly guesses \texttt{yes}/\texttt{no}. Given the number of configurations presented, we only include $F_1$ scores for reasons of space; however, we remark that the Precision and Recall scores were in general quite balanced. The best results were obtained using the features from \textsc{r}, where, as can be expected, prediction performs best when knowledge of changes in the historical results of the input query is available. The features from sets \textsc{q} and \textsc{p} -- which do not assume the availability of such information -- obtain a significantly lower $F_1$-score; the best result including \textsc{r} was with \textsc{pr} ($F_1 = 0.831$) using Linear SVM and window size 17, while the best results without \textsc{r} was with \textsc{q} ($F_1 = 0.60$) using Linear SVM and window size 5.

>>>>

\paragraph{Results:} Table~\ref{tab:classifier} shows the $F_1$-score for the predictions made considering the union of different combinations of the sets of features (\textsc{q}, \textsc{p}, \textsc{r}) and varying the window sizes (3, 5, 9, 17); for reference, we include a baseline that randomly guesses \texttt{yes}/\texttt{no} generating random predictions by respecting the training set’s class distribution. Given the number of configurations presented, we only include $F_1$ scores for reasons of space; however, we remark that the Precision and Recall scores were in general quite balanced. The best results were obtained using the features from \textsc{r}, where, as can be expected, prediction performs best when knowledge of changes in the historical results of the input query is available. The features from sets \textsc{q} and \textsc{p} -- which do not assume the availability of such information -- obtain a significantly lower $F_1$-score; the best result including \textsc{r} was with \textsc{pr} ($F_1 = 0.831$) using Linear SVM and window size 17, while the best results without \textsc{r} was with \textsc{q} ($F_1 = 0.60$) using Linear SVM and window size 5.
